DALEX

### 2021-02-23 DALEX.Rmd
slight changes

---
title: "DALEX"
author: "Scott Coffin"
date: "2/19/2021"
output: 
  html_document:
    code_folding: hide
    theme: sandstone
    toc: yes
    toc_float: yes
    toc_depth: 5
    number_sections: true
  word_document:
    toc: yes
---
```{r global-options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      warning=FALSE, message=FALSE, echo = FALSE)
```

@@

# fill alpha relative to sensitivity/specificity by proportional outcomes within reference groups (see dplyr code above as well as original confusion matrix for comparison)
ggplot(data = plotTable, mapping = aes(x = Reference, y = Prediction, fill = prop)) +
  geom_tile() +
  geom_text(aes(label = Freq), vjust = .5, fontface  = "bold", alpha = 1) +
  scale_fill_gradient(low = "white", high = "cyan4", name = "Proportion") +
  scale_x_discrete(labels = c("No Effect", "Effect")) +
  scale_y_discrete(labels = c("No Effect", "Effect"))
  theme_bw() +
  xlim(rev(levels(table$Reference)))
```

>>>>

---
title: "DALEX"
author: "Scott Coffin"
date: "2/22/2021"
output: 
  html_document:
    code_folding: hide
    theme: sandstone
    toc: yes
    toc_float: yes
    toc_depth: 6
    number_sections: true
  word_document:
    toc: yes
---
```{r global-options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      warning=FALSE, message=FALSE, echo = FALSE)
```

@@

# fill alpha relative to sensitivity/specificity by proportional outcomes within reference groups (see dplyr code above as well as original confusion matrix for comparison)
ggplot(data = plotTable, mapping = aes(x = Reference, y = Prediction, fill = prop)) +
  geom_tile() +
  geom_text(aes(label = Freq), vjust = .5, fontface  = "bold", alpha = 1) +
  scale_fill_gradient(low = "white", high = "cyan4", name = "Proportion") +
  scale_x_discrete(labels = c("No Effect", "Effect")) +
  scale_y_discrete(labels = c("No Effect", "Effect")) +
  theme_bw()
```
